---
title: "Lab2"
author: "Kevin Gnaster, Zach Josten, Cade Balvanz, Zach Lang"
date: "2/16/2022"
output: html_document
---

### Git Hub Repo Link

https://github.com/ZachJosten/Practice2Chocolate

```{r}
library(classdata)
library(ggplot2)
choco <- read.csv("https://ds202-at-isu.github.io/labs/data/choco.csv")
head(choco)
summary(choco)
```

# Question set 1

### 1
```{r}
dim(choco)[1]
```

### 2
```{r}
ggplot(choco, aes(x = as.factor(Review.Date))) + 
  geom_bar() + 
  ggtitle("Bar Plot of Ratings Per Year") + 
  ylab("Amount of Ratings") +
  xlab("Date")
```

# Question Set 2

### 1

```{r}
ggplot(choco, aes(x = Rating)) + 
  geom_histogram(bins = 10) + 
  ggtitle("Histogram of Ratings") + 
  ylab("Amount of Ratings") +
  xlab("Rating")
```

There appears to be some outliers around 1 and 2. The majority of Ratings fall around 3 and 4.

### 2

```{r}
ggplot(data = choco, aes(x = Rating, y = Cocoa.Pct)) +
  geom_point()
```

Cocoa Percentage doesn't seem to effect Ratings significantly.

### 3

```{r}
library(dplyr)
```

```{r}
choco2 = filter(choco, Company.Location %in% c("U.S.A.", "France", "Canada"))

ggplot(data = choco2, aes(x = Rating)) + 
  geom_histogram(bins = 10) + 
  facet_wrap(~Company.Location)
```

Ratings appear to be  higher in the US compared to France and Canada.
\
\
Question we investigated: \
What are the average cocoa percentages of each country where there is chocolate produced?
\

```{r}

company.unique = unique(choco$Company.Location)
cocoa.mean = tapply(choco$Cocoa.Pct,choco$Company.Location, mean)
levels.reorder = levels(reorder(company.unique, cocoa.mean, na.RM=TRUE))
choco.company = company.unique
choco.company.reorder = factor(choco.company, levels = levels.reorder)
company.unique = choco.company.reorder
company.means = data.frame(company.unique, cocoa.mean)
comp.means = dplyr::filter(company.means, company.means$cocoa.mean >= 73)
ggplot(comp.means, aes(x = company.unique, color=company.unique)) + geom_bar(aes(weight = cocoa.mean)) + coord_flip() + xlab("Company Location") + ylab("Cocoa Percent")
```
\
This shows all the Company locations with an average cocoa percentage higher than 73. 73 was chosen as any lower and the graph becomes difficult to read. As we can see, chocolates produced in places like the Philippines, Ireland and Colombia contain a high amount of cocoa in them. 
## Need to add question to investigate and paragraph to workflow
